Results from Primary Coding

### 2023-08-29 analysis/practiceCoding_AW.Rmd
Added descriptive labels

#Prelim results and visualisations for d_journals

@@

d_primaryONLY <- d_journals %>%
  filter(coder_id == "AW" | coder_id == "NM") %>%
  filter(journal_empirical == "Yes") %>%
  group_by(journal) %>%
  distinct(journal, .keep_all = TRUE)

@@

 d_PPConly <- d_primaryONLY %>%
   filter(anyPPC == "YES")

@@

#Add COPE status
```{r}
dj_random <- read_csv(here('data','prepareSample','journals', '03 - final', 'journals-random.csv'), show_col_types = F) %>%
  slice_head(n = 108) %>%
  select(`Journal`, 'COPE' = 'COPE (T = member; F = not a member)')

dj_prominent <- read_csv(here('data','prepareSample','journals', '03 - final', 'journals-prominent.csv'), show_col_types = F) %>%
  slice_head(n = 114) %>%
  select('Journal' = `Journal name`, 'COPE' = 'COPE (T = member; F = not a member)' )

dj_cope <- left_join()

#Code from checkData.RMD for extracting JIFs
d_journals_prominent <- left_join(d_journals_prominent, journal_list_prominent_all, by = 'journal')

>>>>

#Prelim results and visualisations for d_journals using Primary coding data only

@@

d_primaryONLY <- d_journals %>%
  filter(coder_id == "AW" | coder_id == "NM") %>% #keeps only entries with primary coder initials from main data tibble d_journals
  filter(journal_empirical == "Yes") %>%          #removes ineligible journals (not empirical)
  group_by(journal) %>%
  distinct(journal, .keep_all = TRUE)             #keeps only distinct journal entries

@@

# Removes journals that do not offer any PPC 
 d_PPConly <- d_primaryONLY %>%
   filter(anyPPC == "YES")

@@

#Add COPE status
```{r}
# Load googlesheet data

dj_prominent <- read_csv(here('data','raw', 'journalList_PROMINENT.csv')) %>% #loads csv of googlesheet data of prominent journals
  slice_head(n = 114) %>%
  select('journal' = 'journal_name', 'COPE' = 'COPE (T = member; F = not a member)' )

dj_random <- read_csv(here('data','raw', 'journalList_RANDOM.csv')) %>% #loads csv of googlesheet data of random journals
  slice_head(n = 108) %>%
  select('journal' = 'journal_name', 'COPE' = 'COPE (T = member; F = not a member)' )

# Combine above CSVs to one tibble

dj_cope <- bind_rows(dj_prominent, dj_random)

# Identify duplicate rows
duplicates <- duplicated(dj_cope)

# Select the duplicate rows
duplicate_rows <- dj_cope[duplicates, ]

# Check if duplicate rows have the same COPE values for journals
for (i in seq_len(nrow(duplicate_rows))) {
  row <- duplicate_rows[i, ]
  id <- row$ID
  value <- row$Value
  same_values <- all(duplicate_rows$Value[duplicate_rows$ID == id] == value)

  if (same_values) {
    cat("Row", i, "with ID =", id, "has the same values in both columns.\n")
  } else {
    cat("Row", i, "with ID =", id, "has different values in both columns.\n")
  }
}

#All 14 duplicated (both sample) journals had consistent COPE status, join with main data tibble:
d_cope <- left_join(d_journals, dj_cope, by = 'journal')

#join() Code from checkData.RMD for importing JIFs and category

d_journals_prominent <- left_join(d_journals_prominent, journal_list_prominent_all, by = 'journal')
